### 2017-03-16 thesis/misc/glossary.tex
Finished obesity metagene direction subsection
Started editing introduction -- tmp commit
Minor edit in intro and methods
Changed all the data set names and removed "'s" - tmp commit
Edited Intro
tmp commit

\newglossaryentry{type1}{
	name=Type I error,
	text=type I error,
	plural=type I errors,
	description={Incorrect rejection of a true null hypothesis; False positive}
}

\newglossaryentry{type2}{
	name=Type II error,
	text=type II error,
	plural=type II errors,
	description={Incorrect retaining of a false null hypothesis; False negative}
}

\newglossaryentry{power}{
	name=Power,
	text=power,
	description={Probability that it will reject a false null hypothesis; It is inversely related to the probability of making a type II error}
}

@@

\newacronym{irs}{IRS}{insulin receptor seubstrate}

@@

\newacronym{ifny}{IFN-$\gamma$}{interferon-$\gamma$}
\newacronym{tgfb}{TGF-$\beta$}{transforming growth factor-$\beta$}

@@

>>>>

\newglossaryentry{type1}{
	name=Type I error,
	text=Type I error,
	plural=Type I errors,
	description={Incorrect rejection of a true null hypothesis; False positive}
}

\newglossaryentry{type2}{
	name=Type II error,
	text=Type II error,
	plural=Type II errors,
	description={Incorrect retaining of a false null hypothesis; False negative}
}

\newglossaryentry{power}{
	name=Power,
	text=power,
	description={Probability that it will reject a false null hypothesis; It is inversely related to the probability of making a Type II error}
}

@@

\newacronym{irs}{IRS}{insulin receptor substrate}
\newacronym{anova}{ANOVA}{analysis of variance}

@@

\newacronym{ifny}{IFN$\gamma$}{interferon-$\gamma$}
\newacronym{ifna}{IFN$\alpha$}{interferon-$\alpha$}
\newacronym{tgfb}{TGF$\beta$}{transforming growth factor-$\beta$}
\newacronym{tnfa}{TNF$\alpha$}{tumour necrosis factor-$\alpha$}
\newacronym{bcat}{BCAT}{$\beta$-catenin}
\newacronym{egfr}{EGFR}{epidermal growth factor receptor}

@@

\newacronym{nzbc}{NZBC}{New Zealand Breast Cancer}
\newacronym{nz}{NZ}{New Zealand}
